---
title: "Assignment Data Analysis"
author: "Kevin Saner, Phillip Gachnang, Raphael Denz"
date: "18 3 2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Starting situation
Description of the dataset.

## To-Do
Description of the tasks.

## Prerequisites
```{r, message=FALSE,warning=FALSE}
library(DescTools) # for CramerV() function
library(haven) # to read SPSS files
library(labelled) # to deal with variable and value labels
library(knitr) # to get the kable() function for nice tables
library(gplots) # to get the plotmeans() function
```


```{r message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls()) # clear workspace, use if needed
dataset = read_sav("npd.sav")

```

# Data Preparation

## Check the dimension and the variables
```{r}
dim(dataset)


```
The dataset contains 247 observations/dimensions and 57 variables.


```{r}
names(dataset)
```
The names of the variables match the questions of the questionnaire.  

A1 is special: Product
D3 and D9 use one-hot encoding


## Response
```{r}
gross_sample_size <- 592
# keep only rows that indicated completeness
dataset <- subset(dataset,!is.na(dataset$COMPLETE))
100 /gross_sample_size * nrow(dataset)

```



## Measurement Levels and Missingness

Check data for missing values.

```{r}
table(sapply(dataset, is.na))


```
There are 2818 missing values in the data set. The values are distributed as follows among the variables:

```{r}
data.frame(colSums(is.na(dataset)))
```


## Missingness of D9IncYes1

# Analysis

## Proportion of Programme Participation

## Satisfaction with product development process

## Association of incubator participation and satisfaction with the product development process

## Number of R+D personnel

## R+D personnel vs participation

## Including Plots (to be deleted, just an example)

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
