---
title: "Assignment Data Analysis"
author: "Kevin Saner, Phillip Gachnang, Raphael Denz"
date: "18 3 2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Starting situation
Description of the dataset.

## To-Do
Description of the tasks.

## Prerequisites
```{r, message=FALSE,warning=FALSE}
library(DescTools) # for CramerV() function
library(haven) # to read SPSS files
library(labelled) # to deal with variable and value labels
library(knitr) # to get the kable() function for nice tables
library(gplots) # to get the plotmeans() function
```


```{r message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls()) # clear workspace, use if needed
dataset = read_sav("npd.sav")

```

# Data Preparation

## Check Dimensions

## Response

## Measurement Levels and Missingness

## Missingness of D9IncYes1

# Analysis

## Proportion of Programme Participation

## Satisfaction with product development process

## Association of incubator participation and satisfaction with the product development process

## Number of R+D personnel

## R+D personnel vs participation

## Including Plots (to be deleted, just an example)

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
